alloscore, ISF 43

### 2023-06-20 talks/ISF_talk/talk.qmd
fix date glitch in run_alloscore, remake
talk update

---
title: "alloscore, ISF 43"
format:
  revealjs: 
    width: 1500
editor: visual
---

## Timeline

@@

------------------------------------------------------------------------

@@

@@

>>>>

---
title: "alloscore, ISF 43"
format:
  revealjs: 
    width: 1500
revealjs-plugins:
  - attribution
editor: visual
---

## {.nostretch}

![hubs](hub_timeline.png){}

::: {.attribution}
Figure credits: Alex Vespignani and Nicole Samay
:::

@@

## Sharing Business

@@

## Data workflow

```
# A tibble: 12 × 9
    time model forecast         ys            K xdf              score_raw score_oracle score
   <int> <chr> <list>           <list>    <dbl> <list>               <dbl>        <dbl> <dbl>
 1     1 m1    <tibble [4 × 7]> <dbl [4]>   400 <tibble [4 × 8]>      62.5          0    62.5
 2     1 m1    <tibble [4 × 7]> <dbl [4]>   450 <tibble [4 × 8]>      50.0          0    50.0
 3     2 m1    <tibble [4 × 7]> <dbl [4]>   400 <tibble [4 × 8]>     150.          27.3 122. 
 4     2 m1    <tibble [4 × 7]> <dbl [4]>   450 <tibble [4 × 8]>     137.           0   137. 
 5     3 m1    <tibble [4 × 7]> <dbl [4]>   400 <tibble [4 × 8]>      62.2          0    62.2
 6     3 m1    <tibble [4 × 7]> <dbl [4]>   450 <tibble [4 × 8]>      49.7          0    49.7
 7     1 m2    <tibble [4 × 7]> <dbl [4]>   400 <tibble [4 × 8]>      54.8          0    54.8
 8     1 m2    <tibble [4 × 7]> <dbl [4]>   450 <tibble [4 × 8]>      40.2          0    40.2
 9     2 m2    <tibble [4 × 7]> <dbl [4]>   400 <tibble [4 × 8]>     157.          27.3 130. 
10     2 m2    <tibble [4 × 7]> <dbl [4]>   450 <tibble [4 × 8]>     149.           0   149. 
11     3 m2    <tibble [4 × 7]> <dbl [4]>   400 <tibble [4 × 8]>      74.9          0    74.9
12     3 m2    <tibble [4 × 7]> <dbl [4]>   450 <tibble [4 × 8]>      70.9          0    70.9
```

```
> a_series_slim$xdf[[9]]
# A tibble: 4 × 8
  target_names     x score_fun     y oracle components_raw components_oracle components
  <chr>        <dbl> <list>    <dbl>  <dbl>          <dbl>             <dbl>      <dbl>
1 A             80.4 <fn>       55.0   51.5             0               3.52      -3.52
2 B             92.2 <fn>      250.   234.            157.             16.0      141.  
3 C            106.  <fn>       89.2   83.5             0               5.70      -5.70
4 D            122.  <fn>       33.5   31.3             0               2.14      -2.14
```

@@

## General Disclaimer

This is **post-hoc** analysis

Hub forecasters were unaware of

- an allocation score (on joint forecast)
- any allocation based loss
- our quantile interpolation/extrapolation methods (`distfromq`)

  - might be especially important for tails
